---
title: "Jassi"
output: html_document
date: "2023-04-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 11.4 Forecasting Australian domestic tourism

We will compute forecasts for the Australian tourism data . We use the data up to the end of 2015 as a training set, withholding the final two years (eight quarters, 2016Q1–2017Q4) as a test set for evaluation. The code below demonstrates the full workflow for generating coherent forecasts using the bottom-up, OLS and MinT methods.

The accuracy of the forecasts over the test set can be evaluated using the accuracy() function. We summarise some results using RMSE and MASE.

```{r cars}
library(fpp3)

tourism_full <- tourism |>
  aggregate_key((State/Region) * Purpose, Trips = sum(Trips))

fit <- tourism_full |>
  filter(year(Quarter) <= 2015) |>
  model(base = ETS(Trips)) |>
  reconcile(
    bu = bottom_up(base),
    ols = min_trace(base, method = "ols"),
    mint = min_trace(base, method = "mint_shrink")
  )


fc <- fit |> forecast(h = "2 years")


fc |>
  filter(is_aggregated(Region), is_aggregated(Purpose)) |>
  autoplot(
    tourism_full |> filter(year(Quarter) >= 2011),
    level = NULL
  ) +
  labs(y = "Trips ('000)") +
  facet_wrap(vars(State), scales = "free_y")

fc |>
  filter(is_aggregated(State), !is_aggregated(Purpose)) |>
  autoplot(
    tourism_full |> filter(year(Quarter) >= 2011),
    level = NULL
  ) +
  labs(y = "Trips ('000)") +
  facet_wrap(vars(Purpose), scales = "free_y")

fc |>
  filter(is_aggregated(State), is_aggregated(Purpose)) |>
  accuracy(
    data = tourism_full,
    measures = list(rmse = RMSE, mase = MASE)
  ) |>
  group_by(.model) |>
  summarise(rmse = mean(rmse), mase = mean(mase))


```
