---
title: "R Notebook"
output: html_notebook
---

# Single level approaches

Forecasts of hierarchical or grouped time series involved selecting one level of aggregation and generating forecasts for that level.

It involves

Selecting one level of aggregation and generating forecasts for that level.

Then for obtaining set of coherent forecasts for the rest of the structure these forecasts are

-   Aggregated for higher levels
-   Dis-aggregated for lower levels

## Bottom-up Approach

A simple method for generating coherent forecasts

This approach involves first generating forecasts for each series at the **bottom level**, and then summing these to produce forecasts for all the series in the structure.

```{=tex}
\begin{align*}
  \hat{y}_{AA,h}, ~~\hat{y}_{AB,h}, ~~\hat{y}_{AC,h}, ~~\hat{y}_{BA,h} ~~\text{and} ~~\hat{ y}_{BB,h}
\end{align*}
```
Summing these, we get ℎ-step-ahead coherent forecasts for the rest of the series:

```{=tex}
\begin{align*}
  \tilde{y}_{h} & =\hat{y}_{AA,h}+\hat{y}_{AB,h}
+\hat{y}_{AC,h}+\hat{y}_{BA,h}+\hat{y}_{BB,h}, \\
  \tilde{y}_{A,h} & = \hat{y}_{AA,h}+\hat{y}_{AB,h}+\hat{y}_{AC,h}, \\
\text{and}\quad
  \tilde{y}_{B,h} & = \hat{y}_{BA,,h}+\hat{y}_{BB,h}
\end{align*}
```
For this approach:

-   no information is lost due to aggregation

-   bottom-level data can be quite noisy and more challenging to model and forecast.

## Example: Generating bottom-up forecasts

Aim - national and state forecasts for the Australian tourism data without

disaggregations using regions or the purpose of travel

```{r}
library(fpp3)
tourism
```

```{r}
tourism_states <- tourism |>
  aggregate_key(State, Trips = sum(Trips))
tourism_states
```

```{r}

fcasts_state <- tourism_states |>
  filter(!is_aggregated(State)) |>
  model(ets = ETS(Trips)) |>
  forecast()

# Sum bottom-level forecasts to get top-level forecasts
fcasts_national <- fcasts_state |>
  summarise(value = sum(Trips), .mean = mean(value))
```

```{r}
tourism_states |>
  model(ets = ETS(Trips)) |>
  reconcile(bu = bottom_up(ets)) |>
  forecast()
```

#### Workflow for forecasting aggregation structures

```{r}
data |> aggregate_key() |> model() |>  reconcile() |> forecast()
```

1.  Begin with a `tsibble` object (here labelled `data`) containing the individual bottom-level series.

2.  Define in `aggregate_key()` the aggregation structure and build a `tsibble` object that also contains the aggregate series.

3.  Identify a `model()` for each series, at all levels of aggregation.

4.  Specify in `reconcile()` how the coherent forecasts are to be generated from the selected models.

5.  Use the `forecast()` function to generate forecasts for the whole aggregation structure.
